    \documentclass{article}
    \usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{geometry}
\usepackage{hyperref}
\usepackage{enumitem}
\geometry{margin=1in}
\setlength{\parskip}{1em}
\setlength{\parindent}{0pt}

\begin{document}

\begin{center}
    {\LARGE \textbf{Anjitesh Shandilya}}\\[0.5em]
    \href{https://linkedin.com/in/ianjiteshan}{LinkedIn - linkedin.com/in/ianjiteshan} \\
    \href{https://github.com/ianjiteshan}{Github - github.com/ianjiteshan}
\end{center}

Anjitesh Shandilya, a Bachelor of Technology student at the University School of Information, Communication and Technology, specializes in web development, full-stack development, machine learning, and AI. Combining strong technical expertise with excellent time management and organizational skills, he is well-equipped to tackle challenges and excel in dynamic, tech-driven environments.

\section*{EDUCATION}

\begin{itemize}[leftmargin=*]
    \item \textbf{University School of Information, Communication and Technology} \\
    Bachelor of Technology - Information Technology \\
    Delhi, India \\
    November 2022 -- Present
    
    \item \textbf{Kendriya Vidyalaya Vikaspuri} \\
    12th CBSE - $93\%$ \\
    New Delhi \\
    April 2020 -- March 2022
    
    \item \textbf{Delhi International School, Dwarka Sec23} \\
    10th CBSE - $93\%$ \\
    New Delhi \\
    April 2007 -- March 2020
\end{itemize}

\section*{SKILLS SUMMARY}

\begin{itemize}[leftmargin=*]
    \item \textbf{Languages:} C, C++, Ruby, JavaScript, Java, Python, MATLAB
    \item \textbf{Frameworks:} ReactJS, NodeJS, Ruby on Rails, AngularJS, Django, Flask, Spring Boot, TensorFlow, PyTorch, Scikit-learn
    \item \textbf{Database:} MongoDB, MySQL, SQL, MS Access, Firebase
    \item \textbf{AI/ML Tools \& Technologies:} TensorFlow, PyTorch, Scikit-learn, Keras, OpenCV, NLTK, Pandas, NumPy, Matplotlib, Seaborn
    \item \textbf{Soft Skills:} Leadership, Adaptability, Event Management, Time Management
    \item \textbf{Other Skills:} Frontend Responsive Design, Backend, APIs, MERN Web Development, AI/ML Enthusiast, AWS, CAD
\end{itemize}

\section*{PROFESSIONAL EXPERIENCE}

\subsection*{AI ML Intern, IBM-CSRbox}

July 2024 -- August 2024

\begin{itemize}[leftmargin=*]
    \item Collaborated with cross-functional teams to implement data-driven algorithms and models using Python, enhancing the accuracy of machine learning systems.
    \item Developed software solutions to address business challenges by applying data structures and algorithms, resulting in increased efficiency in predictive analytics tasks.
    \item Participated in code reviews and debugged existing modules to optimize ML workflows, improving overall system performance.
    \item Implemented preventive maintenance strategies, resulting in a 20\% decrease in downtime.
\end{itemize}

\subsection*{Web Development Intern, NexusLogic Technologies}

\begin{itemize}[leftmargin=*]
    \item Developed dynamic, responsive user interfaces with JavaScript and React.
    \item Assisted in scalable web app development using Node.js and Java.
    \item Conducted unit testing and supported CI pipelines to ensure software quality.
\end{itemize}

\subsection*{Web Development Intern, Younity}

July 2024 -- August 2024

\subsection*{Data Analyst Intern, RINEX}

Jan 2024 -- March 2024

\subsection*{Marketing Intern, edernity}

Jan 2022 -- Present

\subsection*{Freelance Development and AIML Projects}

\section*{POSITION OF RESPONSIBILITIES}

\subsection*{Association for Computing Machinery, ACM USS}

Video Lead and Executive member \\
Nov 2022 -- Present

Managed team, created promotional materials, and organized successful events, showcasing strong design, creativity and leadership skills.

\subsection*{ALCOM - Alumni Committee USS}

Graphics Team \\
Dec 2022 -- Nov 2023

Event Management and Graphics designing: Manages various talk shows, alumni meet and other events. Used Canva and Adobe Illustrator to make presentations, posters and social media posts.

\subsection*{Techspace}

Graphics Designer \\
Jan 2023 -- Nov 2023

Designing: Created 30+ posts for the club Techspace which has around 700 members. Promoted and successfully handled some events.

\subsection*{Training and Placement Cell}

Placement Coordinator \\
Jan 2023 -- Feb 2024

Managed a student database with academic records, resumes, contacts, and career preferences, supporting resume preparation, interview practice, and career guidance for holistic professional growth.

\subsection*{Harita - Environmental Society of USS}

Graphics Lead and Designer \\
Nov 2022 -- Mar 2024

Led graphics team for Nature Club, creating 20+ posts and news-shorts. Promoted events like tree plantations, bird watching, wildlife talks, and nature walks.

\section*{CERTIFICATIONS}

\begin{itemize}[leftmargin=*]
    \item CyberSecurity Foundation Professional Certificate - CSFPC
    \item Participated in Girl Script Summer of Code 2023
    \item Participated in Girl Script Summer of Code 2024
    \item Several techstack certifications from letsupgrade
    \item Web Development Bootcamp - Udemy (Issued: August 2022)
    \item Advanced OfficeSuite Certification - Microsoft (Issued: April 2023)
    \item Several work simulations from job forage
\end{itemize}

\section*{PROJECTS}

\subsection*{Piston Exclusives}

Spearheaded brand creation, product design, and market positioning, catering to automotive enthusiasts with unique, high-quality apparel. Successfully built a niche brand recognized for its innovative approach to blending fashion with automotive culture.

\subsection*{withU247 - Mental Health App}

The WithU247 Mental Health App is a comprehensive platform designed to support users in managing their mental well-being. \\
Tech: React Native, Node.js, MongoDB, Firebase Authentication, AWS, Git and GitHub

\subsection*{AttendUS - A Web based Attendance App}

A web based attendance monitoring solution which will give overall summary of a student's attendance along with proper subject wise analysis. \\
Tech: HTML, CSS, DB

Making several AI/ML projects.

\end{document}